---
title: "quasispectral"
author: "Dirk Moore"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quasispectral-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Using quasispectral
To download the library, first install the "devtools" package, which will allow you to install packages from github; this only needs to be done once:

`install.packages("devtools")`

Then install the quasispectral package from github:

`devtools::install_github("mooredf22/quasispectral")`

This will make the functions and data in the package available to you in R.

Next, load the libraries; the libraries `QuasiSeq` and `fdrtool` must have been previously installed from CRAN.
```{r, echo=TRUE}
library(QuasiSeq)
library(fdrtool)
library(quasispectral)

```
The first few lines of the data may be examined:
```{r, echo=TRUE}
head(spectralData_CLN1_late)
```
The first column is the gene name, the next 6 columns are spectral counts for mutant animals, and the final 6 columns are counts for wildtype animals.

Finally, call the package as follows, and look at the first few lines of output:
```{r, echo=TRUE}
result.QLfit <- quasiSpectral(spectralDataAll=spectralData_CLN1_late, n.mut=6, n.wt=6)
```
```{r, echo=TRUE}
QLfit.out <- result.QLfit$QLfit
head(QLfit.out)
```
To see the estimated proportion of null samples in the population, from `fdrtool`, look at `eta0`:

```{r, echo=TRUE}
result.QLfit$eta0     # estimated proportion of null samples in population
```
